---
title: "RMarkDown Plotly Ex"
author: "Guillermo Cuenca"
date: "22 de octubre de 2016"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown & Plotly

Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. 

Webpage must contain the date that you created the document, and it must contain a plot created with Plotly.

## Kind of Graphs

- Basic Scatterplot
- Color Scatterplot
- Multy Color Scatterplots
- Heatmap
- Graph Volcainplot

## Basic Scatterplot

```{r, echo = FALSE, message=FALSE}
library(plotly)
plot_ly(mtcars, x = ~wt, y = ~mpg, mode = "markers")
```

## Color Scatterplot

```{r, echo = FALSE, message=FALSE}
library(plotly)
set.seed(100)
d <- diamonds[sample(nrow(diamonds), 1000), ]
plot_ly(d, x = ~carat, y = ~price, color = ~carat,
        size = ~carat, text = ~paste("Clarity: ", clarity))
```

## Multy Color Scatterplots

```{r, echo = FALSE, message=FALSE}
p <- ggplot(data = d, aes(x = carat, y = price)) +
  geom_point(aes(text = paste("Clarity:", clarity))) +
  geom_smooth(aes(colour = cut, fill = cut)) + facet_wrap(~ cut)

ggplotly(p)
```

## Heatmap

```{r, echo = FALSE, message=FALSE}
plot_ly(z = volcano, colorscale = "Greys", type = "heatmap")
```

## Graph Volcainplot

```{r, echo = FALSE, message=FALSE}
plot_ly(z = ~volcano, type = "surface")
```

## Observations

- This plots are taken from https://plot.ly/r/ 
- I´m in process to understand why is showing in page 4/9 warnings about plotly and ggplot versions
- In some times in volcainplot need to pass mouse over layout to see

Thanks
